An Overview of Distributed Version Control Systems

### 2010-06-08 laarsample.tex
cambio de titulo
Cambios cosméticos menores. Agregados algunos paragraph breaks necesarios. Corrreción en la parte de historia. Pushing y Pulling no son más subsecciones, quedaba mal.

\title{Distributed Version Control Systems}
\author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
%\author{Demian Alonso, Bruno Bonnano, Nicol\'{a}s Calligaro and Nicol\'{a}s Perez Santoro}
\maketitle

@@

The concept of distributed repositories came up first on the commercial product 
Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
on to design BitKeeper, another commercial VCS which expanded on those ideas. 
BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
the license to use BitKeeper was finished. 
To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
Linus Torvalds \cite{linusgit} and Mercurial, both now mature DVCS. 
Other open source DVCS in use today are Bazaar, 
developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
the idea of tracking only patches and not versions.

@@

A DVCS has many features that makes it perfect for distributed and non-distributed developments. Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

@@

\subsection{Small, Coherent and Logical Commits}
Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions. The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code. Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.

\subsection{Tagging and Branching}
Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version. Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag

\subsection{Merging}
The merging process has two possible scenarios:
\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
The merging process\cite{svnmerging} between branches preserves all the history of 
both branches on many DVCS tools.

\subsection{Pushing and pulling}
When we want to share our work with the rest of the team we have two basic commands, 
\emph{push} and \emph{pull}.

\subsection{Pushing}
The push process refers to taking all the changes previously selected and adding them to the repository of another peer. In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too. This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team. Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.

\subsection{Pulling}
Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''. The fetch command takes the changes from a peer's repository and copies them to the local repository. After that, the merge process combines the changes you've just downloaded with the ones on your local repository. You can do those two actions separately or altogether by using the ``pull'' command.

>>>>

\title{An Overview of Distributed Version Control Systems}
\author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
%\author{Demian Alonso, Bruno Bonnano, Nicol\'{a}s Calligaro and Nicol\'{a}s Perez Santoro}
\maketitle

@@

The concept of distributed repositories came up first on the commercial product 
Sun TeamWare. Larry McVoy, who worked on Sun Teamware, later went 
on to design BitKeeper, another commercial VCS which expanded on those ideas. 
BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
the license to use BitKeeper was finished. 
To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
Linus Torvalds \cite{linusgit}) and Mercurial, both now mature DVCS. 
Other open source DVCS in use today are Bazaar, 
developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
the idea of tracking only patches and not versions.

@@

A DVCS has many features that makes it perfect for distributed and non-distributed developments. Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

@@

\subsection{Small, Coherent and Logical Commits}
Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions.

The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code. Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.

\subsection{Tagging and Branching}
Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version. Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag.

\subsection{Merging}
The merging process has two possible scenarios:

\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.

\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
The merging process\cite{svnmerging} between branches preserves all the history of 
both branches on many DVCS tools.

\subsection{Pushing and pulling}
When we want to share our work with the rest of the team we have two basic commands:
%\emph{push} and \emph{pull}.

\emph{Push:}
The push process refers to taking all the changes previously selected and adding them to the repository of another peer. In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too.

This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team. Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.

\emph{Pull:} 
Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''. The fetch command takes the changes from a peer's repository and copies them to the local repository. After that, the merge process combines the changes you've just downloaded with the ones on your local repository. You can do those two actions separately or altogether by using the ``pull'' command.
